### 2015-02-20 fundamentals/examples.tex
missing of
nouns

The success of the \Cyclus simulator can be measured in many ways.
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus
ecosystem at multiple institutions indicates that a fuel cycle simulator can
advance in a community-driven development paradigm. Additionally, simulation
results for both once-through and more complex recycling scenarios demonstrate that
\Cyclus possesses the fundamental fuel cycle simulation capabilities to
contribute to the field.

@@

Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})
have been
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the
\Cyclus ecosystem. These archetypes provide the first examples of
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separation, fabrication, storage
facilities, and expanded institutional paradigms.

@@

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the 1-pass recycle case are shown in Figure
\ref{fig:flowmodopen}.

>>>>

The success of the \Cyclus simulator can be measured in many ways.
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus
ecosystem at multiple institutions indicates that a fuel cycle simulator can
advance in this community-driven development paradigm. Additionally, simulation
results for both once-through and more complex recycling scenarios demonstrate that
\Cyclus possesses the fundamental fuel cycle simulation capabilities to
contribute to the field.

@@

Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})
have been
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the
\Cyclus ecosystem. These archetypes provide the first examples of
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separations logic, fuel
fabrication processing, storage facilities, and expanded institutional paradigms.

@@

Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the 1-pass recycle case are shown in Figure
\ref{fig:flowmodopen}.
